Technical Report

### 2018-06-06 fully-abstract-comp/technical-report.tex
Answer for one of Dominique's comments.

\dominique{Remaining question: what exactly does $\nsubsim$ on a UPred mean?  Does it mean subset ``up to n (including)'' or ``up to n-1 (including)''?
  Check what we can require without breaking contractiveness of recursive definition of value relation and/or what we did in previous paper and/or what we need in FTLR proof.
  Update: in the FTLR proof, we seem to need ``up to n'' because the heap predicate of the standard region is contractive in terms of the value relation.
  This also means we can afford to use ``up to n'' without breaking contractiveness of the recursive definition of the value relation.
  }
We have the following notion of regions being an $n$-subset of another region.
\begin{mathpar}
  \inferrule{ \forall \hat{W} \ldotp H \; \hat{W} \nsubsim H' \; \hat{W}}
            { (v,H) \nsubsim (v',H') }
\and
  \inferrule{ \forall \hat{W} \ldotp H \; \hat{W} \nsubsim H' \; \hat{W}}
            { (\pure,H,H_\sigma) \nsubsim (v',H') }
\and
  \inferrule{ \forall \hat{W} \ldotp H \; \hat{W} \nsubsim H' \; \hat{W}}
            { (v,H) \nsubsim (\pure,H',H_\sigma) }
\and
  \inferrule{ \forall \hat{W} \ldotp H \; \hat{W} \nsubsim H' \; \hat{W}}
            { (\pure,H,H_\sigma) \nsubsim (\pure,H',H_\sigma') }
\end{mathpar}
We define $n$-equality of regions $\iota \nsim \iota'$ as the symmetric closure, i.e. $\iota \nequal \iota'$ iff $\iota \nsubsim \iota'$ and $\iota \nsupsim \iota'$.

>>>>

\dominique{Remaining question: what exactly does $\nsubsim$ on a UPred mean?  Does it mean subset ``up to n (including)'' or ``up to n-1 (including)''?
  Check what we can require without breaking contractiveness of recursive definition of value relation and/or what we did in previous paper and/or what we need in FTLR proof.
  Update: in the FTLR proof, we seem to need ``up to n'' because the heap predicate of the standard region is contractive in terms of the value relation.
  This also means we can afford to use ``up to n'' without breaking contractiveness of the recursive definition of the value relation.
  }\\
\lau{You cannot take $\nsubsim$ on a UPred. It only works on regions. We use the
  special notation to signify that it is almost like standard $n$-equality. I suppose
  you are thinking of $\nequal$ for UPreds? The way I have seen it before, it is defined as
``up to $n-1$ (including)''. More precisely: Define the $k$-cut of $p \in \UPred{A}$ to be
\newcommand{\floor}[1]{\lfloor #1 \rfloor}
\newcommand{\kcut}[2][k]{\floor{#2}_{#1}}
  \[
  \kcut{p} = \{ (j,a) \in p | j < k \}.
  \]
  We use this to define a family of equivalences $(\nequal)_{n=0}^{\infty}$ to be, for $p$ and $q$ in $\UPred{A}$
  \[
    p \nequal q \textit{ iff } \kcut[n]{p} = \kcut[n]{q}
  \]
  If we pick a different definition, we should check that it is indeed a
  well-defined $n$-equality (for instance, it should be the total relation for $\nequal[0]$).
} We have the following notion of regions being an $n$-subset of another region.
\begin{mathpar}
  \inferrule{ \forall \hat{W} \ldotp H \; \hat{W} \nsubsim H' \; \hat{W}}
            { (v,H) \nsubsim (v',H') }
\and
  \inferrule{ \forall \hat{W} \ldotp H \; \hat{W} \nsubsim H' \; \hat{W}}
            { (\pure,H,H_\sigma) \nsubsim (v',H') }
\and
  \inferrule{ \forall \hat{W} \ldotp H \; \hat{W} \nsubsim H' \; \hat{W}}
            { (v,H) \nsubsim (\pure,H',H_\sigma) }
\and
  \inferrule{ \forall \hat{W} \ldotp H \; \hat{W} \nsubsim H' \; \hat{W}}
            { (\pure,H,H_\sigma) \nsubsim (\pure,H',H_\sigma') }
\end{mathpar}
We define $n$-equality of regions $\iota \nsim \iota'$ as the symmetric closure, i.e. $\iota \nequal \iota'$ iff $\iota \nsubsim \iota'$ and $\iota \nsupsim \iota'$.
